Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-15 WSSSPE1_report/WSSSPE1_summary_report.tex
small fix in intro, fix of cite later

The organizers decided to list 54 of the papers (see Appendix~\ref{sec:papers} for a list of these papers) as significant
contributions to the workshop, a very high acceptance rate but one
that is reasonable, given the goal of broad participation and the fact
that the reports were already self-published. Based on the submissions, the papers were
grouped into three main categories, namely \emph{Developing and
Supporting Software}, \emph{Policy}, and \emph{Communities}. Each
category was associated with a panel and discussion at the
workshop.  Three to four representatives from each submission
category were appointed as panelists, and assigned to read a subset of
the papers in that category and then discuss them in the panel.
The workshop itself consisted of two keynote presentations followed by the 
three panel/discussion sessions.

@@

The question of what ``sustainable'' means in the context of software was
raised (see \S\ref{sec:defining-sustainability}.) The resources at OSS Watch~\cite{osswatch}   discuss what
to look for when choosing software for procurement, or reuse in further software
development. Regardless of the license and development model that will be used,
the future of the project must be considered. Even if a particular piece of
software satisfies today's requirements, will it continue to do so in the
future? Important questions include whether the supplier will still be around in five
years' time, will it still care for its customers' needs, will it be responsive to
bug reports and feature requests? Should you tie your investment to a single
supplier using a proprietary product, or ensure the project uses an OSI-approved
license, and can outlive any single entity if the software is still important.

@@

The following is a partial list of attendees who were recorded on the
Google doc~\cite{WSSSPE1-google-notes} that was being used for live note taking at the workshop, or by the SC13 student volunteers, with some additions also made by the authors of this report.

>>>>

The organizers decided to list 54 of the papers (see Appendix~\ref{sec:papers} for a list of these papers) as significant
contributions to the workshop, a very high acceptance rate but one
that is reasonable, given the goal of broad participation and the fact
that the reports were already self-published. Based on the submissions, the papers were
grouped into three main categories, namely \emph{Developing and
Supporting Software}, \emph{Policy}, and \emph{Communities}. Each
category was associated with a panel and discussion at the
workshop.  Three to four representatives from each submission
category were appointed as panelists, and assigned to read a subset of
the papers in that category and then discuss them in the panel.
The workshop itself consisted of two keynote presentations followed by the 
three panel/discussion sessions.  Notes were collaboratively taken
by the group during the discussion, using a web document~\cite{WSSSPE1-google-notes}.

@@

The question of what ``sustainable'' means in the context of software was
raised (see \S\ref{sec:defining-sustainability}.) The resources at OSS Watch~\cite{osswatch-web}   discuss what
to look for when choosing software for procurement, or reuse in further software
development. Regardless of the license and development model that will be used,
the future of the project must be considered. Even if a particular piece of
software satisfies today's requirements, will it continue to do so in the
future? Important questions include whether the supplier will still be around in five
years' time, will it still care for its customers' needs, will it be responsive to
bug reports and feature requests? Should you tie your investment to a single
supplier using a proprietary product, or ensure the project uses an OSI-approved
license, and can outlive any single entity if the software is still important.

@@

The following is a partial list of attendees who were recorded on the
document~\cite{WSSSPE1-google-notes} that was being used for live note taking at the workshop, or by the SC13 student volunteers, with some additions also made by the authors of this report.
